---
title: "R Notebook"
output: html_notebook
---

# Reading data 
- Best for .csv and other text files. 

```{r}
iris = read.csv("iris.csv")
```


```{r}
iris
```

# Simple exploratory data analysis

```{r}
str(iris)                 # Summarise the structure of the data 
summary(iris)             # Summarize the data
mean(iris$Sepal.Length)   # Print the mean of the sepal length
```


# Exploratory plotting 

```{r}
plot(iris)
```


```{r}
plot(iris$Petal.Length, iris$Petal.Width, col=factor(iris$Species), xlab="Petal length (cm)", ylab="Petal width (cm)")
```

```{r}
hist(iris$Petal.Length, col="black", xlab="Petal length (cm)", main="")
```


# Importing packages 

```{r}
# install.packages("moments")
library("moments")
skewness(iris$Petal.Length)
kurtosis(iris$Petal.Length)
```


# Almost any data type you want - scrape html, open NetCDFs, parse MS Excel sheets, etc. 
```{r}
# install.packages("rvest")
library("rvest")
lego_movie <- read_html("http://www.imdb.com/title/tt1490017/")
lego_movie
```


# ggplot2

```{r}
library("ggplot2")
ggplot(data=iris, aes(x=Sepal.Length)) + geom_histogram() + xlab("Sepal Length (cm)") + facet_grid(Species~.)
```

## Change ggplot themes
```{r}
ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + geom_point() + xlab("Sepal Length (cm)")

ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + geom_point() + xlab("Sepal Length (cm)") + theme_bw()

ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + geom_point() + xlab("Sepal Length (cm)") + theme_classic()

ggplot(data=iris, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) + geom_point() + xlab("Sepal Length (cm)") + theme_light()

```


# Hypothesis tests 

```{r}
ggplot(data=iris) + geom_density(aes(x=Sepal.Length), fill="red", alpha=0.5) + geom_density(aes(x=Petal.Length, fill=Petal.Length), fill="green", alpha=0.5)

t.test(iris$Sepal.Length, iris$Petal.Length)
```


# Machine learning 
## Packages
- MICE (missing values)
- rpart (partition data)
- PARTY (more partitioning of data)
- caret (classification and regression training)
- randomForest (obviously)
- nnet (nural nets)
- e1071 (svm, bagged clustering, fuzzy clustering, etc)

```{r}
library("caret")
Lm_model <- train(Sepal.Length~Sepal.Width + Petal.Length + Petal.Width, data=iris, method = "lm")
summary(Lm_model)

library("randomForest")
Rf_fit<-randomForest(formula=Species~., data=iris)
print(Rf_fit)
importance(Rf_fit)

library("nnet")
nnet_model <- nnet(Species~., data=iris, size = 10)

library("e1071")
svm_model <- svm(Species ~ Sepal.Length + Sepal.Width, data=iris)
plot(svm_model, data = iris[,c(2,3,6)])

```

# The end :)